New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}

### 2020-04-27 Paper/main.tex
back up before new paper

\subsection{Main results}

@@

\section*{Appendix} \label{sec:appendixa}
\addcontentsline{toc}{section}{Appendix A}

\begin{table}[!htbp] \centering
  \caption{TCZ and SPZ cities in China}
    \label{tab:appendix1}
\begin{tabular}{llllllllll}
Province  & City      & Code & TCZ & SPZ & Province     & City          & Code & TCZ & SPZ \\
Anhui     & Hefei     & 3401 & 0   & 0   & Guangdong    & Shanwei       & 4415 & 1   & 1   \\
Anhui     & Wuhu      & 3402 & 1   & 0   & Guangdong    & Heyuan        & 4416 & 0   & 1   \\
Anhui     & Bengbu    & 3403 & 0   & 0   & Guangdong    & Yangjiang     & 4417 & 0   & 1   \\
Anhui     & Huainan   & 3404 & 0   & 0   & Guangdong    & Qingyuan      & 4418 & 1   & 1   \\
Anhui     & Maanshan  & 3405 & 1   & 0   & Guangdong    & Dongguan      & 4419 & 1   & 1   \\
Anhui     & Huaibei   & 3406 & 0   & 0   & Guangdong    & Zhongshan     & 4420 & 1   & 1   \\
Anhui     & Tongling  & 3407 & 1   & 0   & Guangdong    & Chaozhou      & 4421 & 1   & 1   \\
Anhui     & Anqing    & 3408 & 0   & 0   & Guangdong    & Jieyang       & 4424 & 1   & 1   \\
Anhui     & Huangshan & 3409 & 1   & 0   & Guangxi      & Nanning       & 4501 & 1   & 1   \\
Anhui     & Fuyang    & 3412 & 0   & 0   & Guangxi      & Liuzhou       & 4502 & 1   & 1   \\
Anhui     & Liuan     & 3415 & 0   & 0   & Guangxi      & Guilin        & 4503 & 1   & 1   \\
Anhui     & Xuancheng & 3418 & 1   & 0   & Guangxi      & Wuzhou        & 4504 & 1   & 1   \\
Anhui     & Chizhou   & 3417 & 0   & 0   & Guangxi      & Beihai        & 4505 & 0   & 1   \\
Beijing   & Beijing   & 1101 & 1   & 1   & Guangxi      & Yulin         & 4506 & 1   & 1   \\
Chongqing & Chongqing & 5001 & 1   & 1   & Guangxi      & Baise         & 4510 & 0   & 1   \\
Fujian    & Fuzhou    & 3501 & 1   & 1   & Guangxi      & Hechi         & 4508 & 1   & 1   \\
Fujian    & Xiamen    & 3502 & 1   & 1   & Guangxi      & Qinzhou       & 4509 & 0   & 1   \\
Fujian    & Putian    & 3503 & 0   & 1   & Guangxi      & Fangchenggang & 4512 & 0   & 1   \\
Fujian    & Sanming   & 3504 & 1   & 1   & Guangxi      & Guigang       & 4513 & 1   & 1   \\
Fujian    & Quanzhou  & 3505 & 1   & 1   & Guangxi      & Hezhou        & 4516 & 1   & 1   \\
Fujian    & Zhangzhou & 3506 & 1   & 1   & Guizhou      & Guiyang       & 5201 & 1   & 1   \\
Fujian    & Nanping   & 3507 & 0   & 1   & Guizhou      & Liupanshui    & 5202 & 0   & 1   \\
Fujian    & Ningde    & 3508 & 0   & 1   & Guizhou      & Zunyi         & 5203 & 1   & 1   \\
Fujian    & Longyan   & 3509 & 1   & 1   & Guizhou      & Anshun        & 5207 & 1   & 1   \\
Gansu     & Lanzhou   & 6201 & 1   & 1   & Hainan       & Haikou        & 4601 & 0   & 0   \\
Gansu     & Jiayuguan & 6202 & 0   & 1   & Hebei        & Shijiazhuang  & 1301 & 1   & 1   \\
Gansu     & Jinchang  & 6203 & 1   & 1   & Hebei        & Tangshan      & 1302 & 1   & 1   \\
Gansu     & Baiyin    & 6204 & 1   & 1   & Hebei        & Qinhuangdao   & 1303 & 0   & 1   \\
Gansu     & Tianshui  & 6205 & 0   & 1   & Hebei        & Handan        & 1304 & 1   & 1   \\
Gansu     & Jiuquan   & 6206 & 0   & 1   & Hebei        & Xingtai       & 1305 & 1   & 1   \\
Gansu     & Zhangye   & 6207 & 1   & 1   & Hebei        & Baoding       & 1306 & 1   & 1   \\
Gansu     & Wuwei     & 6208 & 0   & 1   & Hebei        & Zhangjiakou   & 1307 & 1   & 1   \\
Gansu     & Dingxin   & 6209 & 0   & 1   & Hebei        & Chengde       & 1308 & 1   & 1   \\
Gansu     & Longnann  & 6210 & 0   & 1   & Hebei        & Cangzhou      & 1309 & 0   & 1   \\
Gansu     & Pingliang & 6211 & 0   & 1   & Hebei        & Langfang      & 1310 & 0   & 1   \\
Gansu     & Qingyangn & 6212 & 0   & 1   & Hebei        & Hengshui      & 1311 & 1   & 1   \\
Guangdong & Guangzhou & 4401 & 1   & 1   & Heilongjiang & Harbin        & 2301 & 0   & 0   \\
Guangdong & Shaoguan  & 4402 & 1   & 1   & Heilongjiang & Qiqihar       & 2302 & 0   & 0   \\
Guangdong & Shenzhen  & 4403 & 1   & 1   & Heilongjiang & Jixi          & 2303 & 0   & 0   \\
Guangdong & Zhuhai    & 4404 & 1   & 1   & Heilongjiang & Hegang        & 2304 & 0   & 0   \\
Guangdong & Shantou   & 4405 & 1   & 1   & Heilongjiang & Shuangyashan  & 2305 & 0   & 0   \\
Guangdong & Foshan    & 4406 & 1   & 1   & Heilongjiang & Daqing        & 2306 & 0   & 0   \\
Guangdong & Jiangmen  & 4407 & 1   & 1   & Heilongjiang & Yichun        & 2307 & 0   & 0   \\
Guangdong & Zhanjiang & 4408 & 1   & 1   & Heilongjiang & Jiamusi       & 2308 & 0   & 0   \\
Guangdong & Maoming   & 4409 & 0   & 1   & Heilongjiang & Qitaihe       & 2309 & 0   & 0   \\
Guangdong & Zhaoqing  & 4412 & 1   & 1   & Heilongjiang & Mudanjiang    & 2310 & 0   & 0   \\
Guangdong & Huizhou   & 4413 & 1   & 1   & Heilongjiang & Heihe         & 2311 & 0   & 0   \\
Guangdong & Meizhou   & 4414 & 0   & 1   & Heilongjiang & Suihua        & 2314 & 0   & 0  

\begin{table}[!htbp] \centering
  \caption{TCZ and SPZ cities in China (continued)}
    \label{tab:appendix2}
\begin{tabular}{llllllllll}
Province       & City         & geocode4\_corr & TCZ & SPZ & Province & City        & geocode4\_corr & TCZ & SPZ \\
Henan          & Zhengzhou    & 4101           & 1   & 1   & Jiangsu  & Xuzhou      & 3203           & 1   & 1   \\
Henan          & Kaifeng      & 4102           & 0   & 1   & Jiangsu  & Changzhou   & 3204           & 1   & 1   \\
Henan          & Luoyang      & 4103           & 1   & 1   & Jiangsu  & Suzhou      & 3205           & 1   & 1   \\
Henan          & Pingdingshan & 4104           & 0   & 1   & Jiangsu  & Nantong     & 3206           & 1   & 1   \\
Henan          & Anyang       & 4105           & 1   & 1   & Jiangsu  & Lianyungang & 3207           & 0   & 1   \\
Henan          & Hebi         & 4106           & 0   & 1   & Jiangsu  & Yancheng    & 3209           & 0   & 1   \\
Henan          & Xinxiang     & 4107           & 0   & 1   & Jiangsu  & Yangzhou    & 3210           & 1   & 1   \\
Henan          & Jiaozuo      & 4108           & 1   & 1   & Jiangsu  & Zhenjiang   & 3211           & 1   & 1   \\
Henan          & Puyang       & 4109           & 0   & 1   & Jiangsu  & Taizhou     & 3212           & 1   & 1   \\
Henan          & Xuchang      & 4110           & 0   & 1   & Jiangsu  & Suqian      & 3217           & 0   & 1   \\
Henan          & Luohe        & 4111           & 0   & 1   & Jiangsu  & Huaian      & 3221           & 0   & 1   \\
Henan          & Sanmenxia    & 4112           & 1   & 1   & Jiangxi  & Nanchang    & 3601           & 1   & 1   \\
Henan          & Shangqiu     & 4113           & 0   & 1   & Jiangxi  & Jingdezhen  & 3602           & 0   & 1   \\
Henan          & Zhoukou      & 4114           & 0   & 1   & Jiangxi  & Pingxiang   & 3603           & 1   & 1   \\
Henan          & Zhumadian    & 4115           & 0   & 1   & Jiangxi  & Jiujiang    & 3604           & 1   & 1   \\
Henan          & Nanyang      & 4116           & 0   & 1   & Jiangxi  & Xinyu       & 3605           & 0   & 1   \\
Henan          & Xinyangn     & 4117           & 0   & 1   & Jiangxi  & Yingtan     & 3606           & 1   & 1   \\
Hubei          & Wuhan        & 4201           & 1   & 1   & Jiangxi  & Ganzhoun    & 3607           & 1   & 1   \\
Hubei          & Huangshi     & 4202           & 1   & 1   & Jiangxi  & Yichun      & 3608           & 0   & 1   \\
Hubei          & Shiyan       & 4203           & 0   & 1   & Jiangxi  & Shangrao    & 3609           & 0   & 1   \\
Hubei          & Yichang      & 4205           & 1   & 1   & Jiangxi  & Jian        & 3610           & 1   & 1   \\
Hubei          & Xiangfan     & 4206           & 0   & 1   & Jiangxi  & Fuzhou      & 3611           & 1   & 1   \\
Hubei          & Ezhou        & 4207           & 1   & 1   & Jilin    & Changchun   & 2201           & 0   & 0   \\
Hubei          & Jingmen      & 4208           & 1   & 1   & Jilin    & Jilin       & 2202           & 1   & 0   \\
Hubei          & Huanggang    & 4209           & 0   & 1   & Jilin    & Siping      & 2203           & 1   & 0   \\
Hubei          & Xiaogan      & 4210           & 0   & 1   & Jilin    & Liaoyuan    & 2204           & 0   & 0   \\
Hubei          & Xianning     & 4211           & 1   & 1   & Jilin    & Tonghua     & 2205           & 1   & 0   \\
Hubei          & Jingzhou     & 4212           & 1   & 1   & Jilin    & Baicheng    & 2209           & 0   & 0   \\
Hubei          & Suizhou      & 4215           & 0   & 1   & Liaoning & Shenyang    & 2101           & 1   & 1   \\
Hunan          & Changsha     & 4301           & 1   & 1   & Liaoning & Dalian      & 2102           & 1   & 1   \\
Hunan          & Zhuzhou      & 4302           & 1   & 1   & Liaoning & Anshan      & 2103           & 1   & 1   \\
Hunan          & Xiangtan     & 4303           & 1   & 1   & Liaoning & Fushun      & 2104           & 1   & 1   \\
Hunan          & Hengyang     & 4304           & 1   & 1   & Liaoning & Benxi       & 2105           & 1   & 1   \\
Hunan          & Shaoyang     & 4305           & 0   & 1   & Liaoning & Dandong     & 2106           & 0   & 1   \\
Hunan          & Yueyang      & 4306           & 1   & 1   & Liaoning & Jinzhou     & 2107           & 1   & 1   \\
Hunan          & Changde      & 4307           & 1   & 1   & Liaoning & Yingkou     & 2108           & 0   & 1   \\
Hunan          & Yiyang       & 4309           & 1   & 1   & Liaoning & Fuxin       & 2109           & 1   & 1   \\
Hunan          & Loudin       & 4310           & 1   & 1   & Liaoning & Liaoyang    & 2110           & 1   & 1   \\
Hunan          & Chenzhou     & 4311           & 1   & 1   & Liaoning & Panjin      & 2111           & 0   & 1   \\
Hunan          & Huaihua      & 4312           & 1   & 1   & Liaoning & Tieling     & 2112           & 0   & 1   \\
Inner Mongolia & Hohhot       & 1501           & 1   & 1   & Liaoning & Chaoyang    & 2113           & 0   & 1   \\
Inner Mongolia & Baotou       & 1502           & 1   & 1   & Ningxia  & Yinchuan    & 6401           & 1   & 1   \\
Inner Mongolia & Wuhai        & 1503           & 1   & 1   & Ningxia  & Shizuishan  & 6402           & 1   & 1   \\
Inner Mongolia & Chifeng      & 1504           & 1   & 1   & Ningxia  & Guyuann     & 6404           & 0   & 1   \\
Inner Mongolia & Hulunbeirn   & 1507           & 0   & 1   & Qinghai  & Xining      & 6301           & 0   & 0   \\
Inner Mongolia & Ulanqabn     & 1510           & 0   & 1   & Shaanxi  & Xian        & 6101           & 1   & 1   \\
Inner Mongolia & Bayannaoern  & 1511           & 0   & 1   & Shaanxi  & Tongchuan   & 6102           & 1   & 1   \\
Jiangsu        & Nanjing      & 3201           & 1   & 1   & Shaanxi  & Baoji       & 6103           & 0   & 1   \\
Jiangsu        & Wuxi         & 3202           & 1   & 1   & Shaanxi  & Xianyang    & 6104           & 0   & 1  

\begin{table}[!htbp] \centering
  \caption{TCZ and SPZ cities in China (continued)}
    \label{tab:appendix3}
\begin{tabular}{llllllllll}
Province       & City         & geocode4\_corr & TCZ & SPZ & Province & City        & geocode4\_corr & TCZ & SPZ \\
Shaanxi  & Weinan    & 6105           & 1   & 1   & Xinjiang & Karamay  & 6502           & 0   & 1   \\
Shaanxi  & Hanzhong  & 6106           & 0   & 1   & Yunnan   & Kunming  & 5301           & 1   & 1   \\
Shaanxi  & Ankang    & 6107           & 0   & 1   & Yunnan   & Zhaotong & 5306           & 1   & 1   \\
Shaanxi  & Shangluon & 6108           & 1   & 1   & Yunnan   & Qujing   & 5303           & 1   & 1   \\
Shaanxi  & Yanan     & 6109           & 0   & 1   & Yunnan   & Simaon   & 5309           & 0   & 1   \\
Shaanxi  & Yulinn    & 6110           & 0   & 1   & Yunnan   & Baoshan  & 5312           & 0   & 1   \\
Shandong & Jinan     & 3701           & 1   & 1   & Yunnan   & Lijiangn & 5314           & 0   & 1   \\
Shandong & Qingdao   & 3702           & 1   & 1   & Yunnan   & Lincangn & 5317           & 0   & 1   \\
Shandong & Zibo      & 3703           & 1   & 1   & Zhejiang & Hangzhou & 3301           & 1   & 1   \\
Shandong & Zaozhuang & 3704           & 1   & 1   & Zhejiang & Ningbo   & 3302           & 1   & 1   \\
Shandong & Dongying  & 3705           & 0   & 1   & Zhejiang & Wenzhou  & 3303           & 1   & 1   \\
Shandong & Yantai    & 3706           & 1   & 1   & Zhejiang & Jiaxing  & 3304           & 1   & 1   \\
Shandong & Weifang   & 3707           & 1   & 1   & Zhejiang & Huzhou   & 3305           & 1   & 1   \\
Shandong & Jining    & 3708           & 1   & 1   & Zhejiang & Shaoxing & 3306           & 1   & 1   \\
Shandong & Taian     & 3709           & 1   & 1   & Zhejiang & Jinhua   & 3307           & 1   & 1   \\
Shandong & Weihai    & 3710           & 0   & 1   & Zhejiang & Quzhou   & 3308           & 1   & 1   \\
Shandong & Rizhao    & 3711           & 0   & 1   & Zhejiang & Zhoushan & 3309           & 0   & 1   \\
Shandong & Liaocheng & 3714           & 0   & 1   & Zhejiang & Lishui   & 3310           & 0   & 1   \\
Shandong & Linyi     & 3713           & 0   & 1   & Zhejiang & Taizhou  & 3311           & 1   & 1   \\
Shandong & Heze      & 3717           & 0   & 1   &          &          &                &     &     \\
Shandong & Laiwu     & 3720           & 1   & 1   &          &          &                &     &     \\
Shanghai & Shanghai  & 3101           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Taiyuan   & 1401           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Datong    & 1402           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Yangquan  & 1403           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Changzhi  & 1404           & 0   & 1   &          &          &                &     &     \\
Shanxi   & Jincheng  & 1405           & 0   & 1   &          &          &                &     &     \\
Shanxi   & Shuozhou  & 1406           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Xinzhou   & 1408           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Luliangn  & 1409           & 0   & 1   &          &          &                &     &     \\
Shanxi   & Jinzhong  & 1417           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Linfen    & 1410           & 1   & 1   &          &          &                &     &     \\
Shanxi   & Yuncheng  & 1412           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Chengdu   & 5101           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Zigong    & 5103           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Panzhihua & 5104           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Luzhou    & 5105           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Deyang    & 5106           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Mianyang  & 5107           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Guangyuan & 5108           & 0   & 1   &          &          &                &     &     \\
Sichuan  & Suining   & 5109           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Neijiang  & 5110           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Leshan    & 5111           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Yibin     & 5114           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Nanchong  & 5113           & 1   & 1   &          &          &                &     &     \\
Sichuan  & Yaan      & 5118           & 0   & 1   &          &          &                &     &     \\
Sichuan  & Guangan   & 5122           & 1   & 1   &          &          &                &     &     \\
Tianjin  & Tianjin   & 1201           & 1   & 1   &          &          &                &     &     \\
Xinjiang & Urumqi    & 6501           & 1   & 1   &          &          &                &     &    

\begin{table}[hbt]\centering
\resizebox{\textwidth}{!}{
\begin{threeparttable}   
\caption{\small SO2 Industry share, 2005}
\begin{tabular}{l*{2}{c}}
\toprule
& \multicolumn{2}{c}{} \\ 
\hline
\\[-1.8ex] & CIC & Value \\ 
\midrule
Non-metallic Mineral Products &	31&	0.2340\\ 
Smelting and Pressing of Ferrous Metals	&32	&0.1983\\ 
Raw Chemical Materials and Chemical Products&	26	&0.1611\\ 
Processing of Petroleum, Coking, Processing of Nuclear Fuel	&25	&0.0910\\ 
Smelting and Pressing of Non-ferrous Metals	&33&	0.0855\\ 
Paper and Paper Products&	22&	0.0577\\ 
Textile	&17	&0.0407\\ 
Chemical Fibers&	28	&0.0222\\ 
Processing of Food from Agricultural Products&	13	&0.0199\\ 
Beverages&	15	&0.0130\\ 
Foods	&14	&0.0123\\ 
Medicines&	27	&0.0089\\ 
General Purpose Machinery	&35&	0.0089\\ 
Processing of Timber, Manufacture of Wood,Bamboo, Rattan, Palm, and Straw Products	&20	&0.0065\\ 
Rubber	&29&	0.0063\\ 
Transport Equipment&	37&	0.0061\\ 
Special Purpose Machinery&	36&	0.0050\\ 
Electrical Machinery and Equipment&	39&	0.0038\\ 
Metal Products&	34	&0.0037\\ 
Leather, Fur, Feather and Related Products	&19	&0.0029\\ 
Communication Equipment, Computers and Other Electronic Equipment&	40&	0.0025\\ 
Textile Wearing Apparel, Footwear, and Caps	&18&	0.0022\\ 
Measuring Instruments and Machinery for Cultural Activity and Office Work	&41&	0.0020\\ 
Plastics&	30&	0.0018 \\ 
Tobacco&	16&	0.0016\\ 
Artwork and Other Manufacturing&	42	&0.0007\\ 
Furniture&	21&	0.0006\\ 
Articles For Culture, Education and Sport Activity&	24&	0.0004\\ 
Printing, Reproduction of Recording Media&	23&	0.0004\\

\hline
\end{tabular}
\begin{tablenotes}
      \small
      \item The share is computed for 28 industries. \\
      Source: MEP dataset. Author's own computation 
    \end{tablenotes}
    \label{tab:so2share}
\end{threeparttable}}
\end{table}

>>>>

\subsection{Main results} \label{sec:main}

@@
